\documentclass[conference]{IEEEtran}

\ifCLASSINFOpdf
\else
\fi

\begin{document}
\title{Android Log-in Application}

\author{\IEEEauthorblockN{Ben Puhalski}
\IEEEauthorblockA{Computer Science\\
Lakehead University\\
Thunder Bay, Ontario P7B 5E1\\
Email: bcpuhals@lakeheadu.ca}}

\maketitle

\begin{abstract}
This report will go through the features, short-comings and bugs-fixes associated with 
this Android Login application.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}

Here I will go over the implementation and the journey that I went through in solving the problem described in section 2.

\section{Problem}
In this application, I would like to implement a solution to this given problem. The problem is to have some sort of method of saving data for multiple users in some application that multiple people may use. Each person should be able to see their saved data without other people being able to access that data. There should also be some way to "sign in" and "sign out" in order to let other users access their data.

\section{Method}
In this implementation I will create an app in android studio using the Kotlin programming language and create an app that will give a solution to the problem. 

\subsection{Layouts}

There are multiple activities in this implementation and therefore are multiple layouts. 

\subsection{Interaction}
\subsubsection{flowchart here}
\subsection{Builds}

\subsection{Translation}



\section{Bugs}

\section{Results}

\subsection{Pros}

\subsection{Cons}

\section{Future Implementation}

\section{Conclusion}
The conclusion goes here.

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}
\newpage
\section{Appendix}

\end{document}
